Job mobility and earnings growth: diffrerent markets, different outcomes.

### 2018-10-12 draft.Rmd
Update draft.Rmd

Worker mobility is a key strategy for improving earnings and conditions. Routinely, authors show how workers make significant gains through quitting or securing promotions. Yet, capitalist countries differ in mobility rates; especially in terms of voluntary mobility. If quitting for a new employer is more common in the UK than Germany, does this mean that German workers are held back from advancing their careers, or does it mean that the nature of quitting is different in both countries? Authors typically rationalise country differences in mobility rates as differences in employment protection legislation (Brown) or differences in job creation and destruction (OECD). This article takes a different approach, and argues that German and British institutions shape not only the likelihood of job mobility, but also the rewards tied to mobility.

>>>>

Job mobility is often framed as a key strategy for improving earnings and conditions. Routinely, authors show how workers make significant gains through quitting or securing promotions yet, capitalist countries differ in mobility rates; especially regarding rates of voluntary mobility. If quitting a job is inherrently beneficial to workers, but more common in the UK than Germany, does this mean that German workers are held back from potential gains, or does it mean that the nature of quitting in both countries is different? Authors typically rationalise country differences in mobility rates as differences in employment protection legislation (Brown) or differences in job creation and destruction (OECD). This article takes a different approach, and shows that German and British institutions shape not only the likelihood of job mobility, but also the rewards tied to mobility.
